\documentclass[10pt,]{article}
\usepackage{lmodern}
\usepackage{setspace}
\setstretch{1.5}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=2.5cm]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Title},
            pdfauthor={Alex Phillips},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{{#1}}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{{#1}}}
\newcommand{\ImportTok}[1]{{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{{#1}}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{{#1}}}
\newcommand{\BuiltInTok}[1]{{#1}}
\newcommand{\ExtensionTok}[1]{{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{{#1}}}
\newcommand{\RegionMarkerTok}[1]{{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
\newcommand{\NormalTok}[1]{{#1}}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\title{Title}
\author{Alex Phillips}
\date{\today}

\begin{document}
\maketitle

Git is about version control. Changes made to files are called commits.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  To set git account locally
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{git} \NormalTok{config --global user.email }\StringTok{"user.email@email.com"}
\end{Highlighting}
\end{Shaded}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  To initialize folder as git repository.
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{git} \NormalTok{init}
\NormalTok{$ }\KeywordTok{git} \NormalTok{status}
\KeywordTok{On} \NormalTok{branch master}

\KeywordTok{Initial} \NormalTok{commit}

\KeywordTok{Untracked} \NormalTok{files:}
  \KeywordTok{(use} \StringTok{"git add <file>..."} \NormalTok{to include in what will be committed}\KeywordTok{)}

        \KeywordTok{.git_workshop_notes.md.swp}
        \KeywordTok{git_workshop_notes.md}
        \KeywordTok{git_workshop_notes.pdf}
        \KeywordTok{git_workshop_notes.tex}
        \KeywordTok{git_workshop_notestex}
        \KeywordTok{git_workshop_notestex.aux}
        \KeywordTok{git_workshop_notestex.log}
        \KeywordTok{git_workshop_notestex.out}
        \KeywordTok{git_workshop_notestex.pdf}

\KeywordTok{nothing} \NormalTok{added to commit but untracked files present (use }\StringTok{"git add"} \NormalTok{to track)}

\end{Highlighting}
\end{Shaded}

\begin{itemize}
\tightlist
\item
  By default, first commit goes to Master.
\item
  Here I have created files, and they are UNTRACKED!!
\item
  As soon as you make git aware of them, git will begin tracking their
  changes.
\item
  git add stages the changes.
\item
  Some people add each file separately, then commit in bulk.
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{git} \NormalTok{add *}
\NormalTok{$ }\KeywordTok{git} \NormalTok{status}
\KeywordTok{On} \NormalTok{branch master}

\KeywordTok{Initial} \NormalTok{commit}

\KeywordTok{Changes} \NormalTok{to be committed:}
  \KeywordTok{(use} \StringTok{"git rm --cached <file>..."} \NormalTok{to unstage}\KeywordTok{)}

        \KeywordTok{new} \NormalTok{file:   git_workshop_notes.md}
        \KeywordTok{new} \NormalTok{file:   git_workshop_notes.pdf}
        \KeywordTok{new} \NormalTok{file:   git_workshop_notes.tex}
        \KeywordTok{new} \NormalTok{file:   git_workshop_notestex}
        \KeywordTok{new} \NormalTok{file:   git_workshop_notestex.aux}
        \KeywordTok{new} \NormalTok{file:   git_workshop_notestex.log}
        \KeywordTok{new} \NormalTok{file:   git_workshop_notestex.out}
        \KeywordTok{new} \NormalTok{file:   git_workshop_notestex.pdf}

\KeywordTok{Untracked} \NormalTok{files:}
  \KeywordTok{(use} \StringTok{"git add <file>..."} \NormalTok{to include in what will be committed}\KeywordTok{)}

        \KeywordTok{.git_workshop_notes.md.swp}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\item
  Now it's tracking them, but they have not been committed yet.
\item
  git commit

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$ }\KeywordTok{git} \NormalTok{commit}
\NormalTok{[}\KeywordTok{opens} \NormalTok{vi editor and wants message with the stuff]}
\NormalTok{[}\KeywordTok{master} \NormalTok{(root-commit) }\KeywordTok{0e0d499}\NormalTok{] Start notes on this tutorial folder}
 \KeywordTok{8} \NormalTok{files changed, 1280 insertions(+)}
 \KeywordTok{create} \NormalTok{mode 100644 git_workshop_notes.md}
 \KeywordTok{create} \NormalTok{mode 100644 git_workshop_notes.pdf}
 \KeywordTok{create} \NormalTok{mode 100644 git_workshop_notes.tex}
 \KeywordTok{create} \NormalTok{mode 100644 git_workshop_notestex}
 \KeywordTok{create} \NormalTok{mode 100644 git_workshop_notestex.aux}
 \KeywordTok{create} \NormalTok{mode 100644 git_workshop_notestex.log}
 \KeywordTok{create} \NormalTok{mode 100644 git_workshop_notestex.out}
 \KeywordTok{create} \NormalTok{mode 100644 git_workshop_notestex.pdf}
\end{Highlighting}
\end{Shaded}
\item
  vi editor is default, but I prefer vim:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{$  }\KeywordTok{git} \NormalTok{config --global user.editor }\StringTok{"vim"}
\end{Highlighting}
\end{Shaded}
\item
  git log tells use the history of changes that we have made. ```bash \$
  git log commit 0e0d499b750312cf8fe371799803dfdb5637d321 Author:
  alexprp
  \href{mailto:alexprphillips@gmail.com}{\nolinkurl{alexprphillips@gmail.com}}
  Date: Thu Feb 25 13:32:33 2016 -0600

  Start notes on this tutorial folder
\end{itemize}

\$ git log --oneline 0e0d499 Start notes on this tutorial folder ```

\begin{itemize}
\item
  This is why it's super important to leave good commit messages.
  Otherwise, the message in the log is meaningless.
\item
  I have made more changes to this notes file and its derivatives since
  we last committed. Let's see what that does ```bash \$ git status On
  branch master Changes not staged for commit: (use ``git add \ldots{}''
  to update what will be committed) (use ``git checkout -- \ldots{}'' to
  discard changes in working directory)

  modified: git\_workshop\_notes.md modified: git\_workshop\_notes.pdf
  modified: git\_workshop\_notes.tex
\end{itemize}

Untracked files: (use ``git add \ldots{}'' to include in what will be
committed)

\begin{verbatim}
.git_workshop_notes.md.swp
\end{verbatim}

no changes added to commit (use ``git add'' and/or ``git commit -a'')
``` - git diff tells us the changes specifically that have been made. -
I don't put that here because it's the same text and
pandoc/latex/markdown get confused.

\hypertarget{refs}{}

\end{document}
